Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-05 paper.tex
Fixed NumPy citation reference

\emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
It is registered on the Python Package Index (PyPI) and can be installed using
\begin{center}
\textbf{\texttt{pip install augraphy}}
\end{center}
\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}. \emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments and supports several recent major versions of Python 3. Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:

>>>>

\emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
It is registered on the Python Package Index (PyPI) and can be installed using
\begin{center}
\textbf{\texttt{pip install augraphy}}
\end{center}
\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{ref_numpy}. \emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments and supports several recent major versions of Python 3. Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:
